Rmarkdown Features

### 2018-03-25 1062_class/Multivariate_Analysis/multi_Rnotes.Rmd
update

Generater covariance and correlation Matricies:
```{r echo=TRUE}
cov(iris[,1:4]) ## Cov Matrix of variable 1~4

```

```{r echo=TRUE}
cor(iris[,1:4]) ## Cor Matrix of variable 1~4
```

>>>>

Generater covariance and correlation Matricies:
```{r echo=TRUE}
library(mat2tex)
cov.mt <- cov(iris[,1:4]) ## Cov Matrix of variable 1~4
cor.mt <- cor(iris[,1:4]) ## Cor Matrix of variable 1~4
```

Covariance matrix 
```{r echo=FALSE, results='asis'}
"$=" %_% xm(cov.mt,2) %_%"$"
```

Correlation matrix 
```{r echo=FALSE, results='asis'}
"$=" %_% xm(cor.mt,2) %_%"$"
```

### 2018-03-25 Instructions/Rmarkdown_features/rmd_features.rmd
update

---
title: "Rmarkdown Features"
subtitle: "This is subtitle"
author: Yongfu Liao
date: March 18, 2018
bibliography: ./citation/neanderthals.bib
csl: ./citation/apa-no-doi-no-issue.csl
link-citations: yes
output:
  html_document:
    css: ../style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 4
    toc_float: true
---

@@

## yaml Setup {.tabset}
Include the code in yaml header.

@@

## Dynamic Variables

@@

## $\LaTeX$ Rendering {.tabset}

### Passing Matrix Object

@@

![](mat2tex.png){width=60% height=auto}

@@

## Citations 
To include **Citations**, [Read this](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html){target="_blank"}.

@@

## Emphasis {.tabset}

@@

## Footnotes with Paragraphs
Check [Pandoc](http://pandoc.org/MANUAL.html#footnotes){target="_blank"} for details.

@@

## Shaped Images {.tabset}

### Rounded Edge
```{html}
<div class="rounded">
![](../icons/jekyll_dark.ico){width=auto height="30%"}
</div>
```
<div class="rounded">
![](../icons/jekyll_dark.ico){width=auto height="30%"}
</div>

### Circle Image
```{html}
<div class="circle">
![](../icons/jekyll_dark.ico){width=auto height="30%"}
</div>
```
<div class="circle">
![](../icons/jekyll_dark.ico){width=auto height="30%"}
</div>

<!-- footnotes -->
[^css]: Look at my [stylesheet](https://github.com/liao961120/local_depend/blob/master/style_sheets/style.css){target="_blank"} for syntax details.

@@

[^red]: `.red` is also a self-defined class in my stylesheet.
<!-- footnotes -->

<!-- syntax for Reference section --> 
## References

>>>>

---
title: "Rmarkdown Features"
subtitle: "This is subtitle"
author: Yongfu Liao
date: March 18, 2018
bibliography: /Users/user/local_depend/citation/neanderthals.bib
csl: /Users/user/local_depend/style_sheets/apa-no-doi-no-issue.csl
link-citations: yes
output:
  html_document:
    css: /Users/user/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 4
    toc_float: true
---

@@

yaml Setup {.tabset}
-----------------------------
Include the code in yaml header.

@@

Dynamic Variables
-----------------------------

@@

$\LaTeX$ Rendering {.tabset}
-----------------------------
### Passing Matrix Object

@@

![](mat2tex.png){width=85% height=auto .rounded}

@@

Citations 
-----------------------------

To include **Citations**, [Read this](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html){target="_blank"}.

@@

Emphasis {.tabset}
-----------------------------

@@

Footnotes with Paragraphs
-----------------------------
Check [Pandoc](http://pandoc.org/MANUAL.html#footnotes){target="_blank"} for details.

@@

Shaped Images {.tabset}
-----------------------------

### Rounded Edge
```{html}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}
```
![](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .rounded}

### Circle Image
```{html}
![](../../local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}
```
![This is figure Caption](/Users/user/local_depend/icons/libreoffice.ico){width=auto height="30%" .circle}

<!-- footnotes ---------------------------- -->
[^css]: Look at my [stylesheet](https://github.com/liao961120/local_depend/blob/master/style_sheets/style.css){target="_blank"} for syntax details.

@@

[^red]: `.red` is also a self-defined class in my stylesheet.
<!-- footnotes -------------------------- -->

<!-- syntax for Reference section -->

Figures
-----------------------------

### Captions
Include `fig.cap='An Caption of the Plot'` in the code chunk option gives:
```{r fig.cap='An Caption of the Plot'}
library(ggplot2)
ggplot(iris)+
    geom_point(aes(x=Sepal.Length, y=Sepal.Width, color=Species))
```

References
-----------------------------
